\LARGE Coursework \\ Module Name (CMM536)

### 2018-04-27 submission.Rnw
added references to document

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
<<eval=FALSE>>=
num_attributes <- ncol(df_train)
#build a parameter grid
# Random forest
mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
nodesize <- c( 3, 5, 20)
ntree <- c(200)

PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
                                         ntree=ntree, stringsAsFactors=F))
@
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
<<eval=FALSE>>=
for (i in c(1:nrow(PG))){
  mtry <- PG[i, "mtry"]
  nodesize <- PG[i, "nodesize"]
  ntree <- PG[i, "ntree"]

@@

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
<<eval=FALSE>>=
#assess best model on test set
PG <- PG%>%
  arrange(desc(Accuracy))

@@

\section{Reproducing Results}

You don't need to have a section called \textbf{Reproducing Results}, your report itself will be the answer for this section.

>>>>

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
<<eval=TRUE>>=
num_attributes <- ncol(df_train)
#build a parameter grid
# Random forest
mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
nodesize <- c( 3, 5, 20)
ntree <- c(200)

PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
                                         ntree=ntree, stringsAsFactors=F))
@
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
<<eval=TRUE>>=
for (i in c(1:nrow(PG))){
  mtry <- PG[i, "mtry"]
  nodesize <- PG[i, "nodesize"]
  ntree <- PG[i, "ntree"]

@@

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
<<eval=TRUE>>=
#assess best model on test set
PG <- PG%>%
  arrange(desc(Accuracy))

@@
